---
title: "Lab 02 - Plastic waste"
author: "Vanessa Gill"
date: "02/08/2021"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read_csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

```{r plastic-waste-all-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)
```

I hadn't given it much thought but I didn't know plastic waste was so high in Trinidad and Tobago. Maybe it's because their islands which makes waste management more difficult.

```{r plastic-waste-by-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.02) +
  facet_wrap (~ continent, ncol = 2) +
  theme(legend.position = "none")
```
It looks like they all have a similar range to each other.

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_density()
```

```{r}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent)) +
  geom_density()
```
```{r}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent, 
                     fill = continent)) +
  geom_density(alpha = 0.1)
```
### Exercise 3

Remove this text, and add your answer for Exercise 3 here.

### Exercise 4

Remove this text, and add your answer for Exercise 4 here.

```{r plastic-waste-violin}
# insert code here
```

### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
# insert code here
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
# insert code here
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
# insert code here
```

```{r plastic-waste-population-coastal}
# insert code here
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
# insert code here
```
